|

### 2021-02-09 supplementary_information.Rmd
Update supplementary_information.Rmd

**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island. Fish data were collected from summer to fall. We screened data through the following procedure:

1. We listed recorded fish species and re-organized species names to be consistent across data sources. We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
1. We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve species identified at the genus level that are rarely observed in the data set (< 100 sites occurrence).
1. For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
1. We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
1. Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as their taxonomic resolutions varied greatly among data sources due to difficulties in identifying species.

**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@wiltonBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@ilepaIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@mpcaDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wdnrGuidelinesAssessingFish2018]. These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined
by U.S. Geological Survey and U.S. Department of Agriculture Natural Resources Conservation Service[@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:

>>>>

**Hokkaido, Japan.** We used data from the Hokkaido Freshwater Fish Database HFish[@fukushimaHokkaidoFreshwaterFish2011; @fukushimaModellingEffectsDams2007], monitoring data at protected watersheds[@comteRivFishTIMEGlobalDatabase2021; @teruiMetapopulationStabilityBranching2018], and primary data collected by the authors[@miyazakiTemporalDynamicsFluvial2016; @teruiThreeEcologicalFactors2016], which collectively cover the entire Hokkaido island. Most data were collected from summer to fall. We screened data through the following procedure:

1. We listed recorded fish species and re-organized species names to make them consistent across data sources. We removed the following species at this stage: (1) identified at the family-level; (2) marine fish species (including species that occasionally use brackish/freshwater habitats).
1. We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species (genus level) that are rarely observed in the data set (< 100 sites occurrence).
1. For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
1. We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
1. Four genera (*Lethenteron*, *Pungitius*, *Rhinogobius*, and *Tribolodon*) were treated as species groups (i.e., spp.) as their taxonomic resolutions varied greatly among data sources due to difficulties in identifying species.

**Midwest, US.** We assembled fish community data collected by the Iowa Department of Natural Resources[@iowadepartmentofnaturalresourcesBiologicalAssessmentIowa2004], Illinois Environmental Protection Agency and Illinois Department of Natural Resources[@illinoisenvironmentalprotectionagencyIllinoisWaterMonitoring2014], Minnesota Pollution Control Agency[@minnesotapollutioncontrolagencyDevelopmentFishbasedIndex2014], and Wisconsin Department of Natural Resources[@wisconsindepartmentofnaturalresourcesGuidelinesAssessingFish2018]. These data sets cover most of Upper Mississippi (Hydrologic Unit Code 2 [HUC 2] , region 07, as defined
by U.S. Geological Survey and U.S. Department of Agriculture Natural Resources Conservation Service[@u.s.geologicalsurveyandu.s.departmentofagriculturenaturalresourcesconservationserviceFederalStandardsProcedures2013]) and the part of Great Lakes (HUC 2, region 04), Missouri (HUC 2, region 10), and Ohio (HUC 2, region 05). Fish data were collected from summer to fall with electrofishing (backpack, barge-type, or boat-mounted) and supplemental netting at some locations. We screened data through the following procedure:
